Innovative Technologies for and Observational Studies of Star and Planet Formation

### 2015-03-25 chSiGaps/AO_bondedSi.tex
remove white space in any \cite{a, b} instances in the Si Gaps paper

Crystalline silicon is an excellent optical material for the infrared. Si has a high refractive index ($3.55-3.45$ from $\lambda = 1150-2500\;$nm at room temperature, \cite{2006SPIE.6273E..77F}) and superb transmission from slightly longer than the equivalent wavelength of its band gap ($\sim$1.15 $\mu$m) to about 6.5 $\mu$m \cite{PhysRev.108.268, PhysRev.78.178} and in the far-IR \cite{doi:10.1117/12.323764}.  It has adequate transmission  ($\alpha \sim 1$ cm$^{-1}$) for many purposes in the 18-30 $\mu$m region as well \cite{doi:10.1117/12.323764}.  There is an extensive industrial infrastructure for the production of ultrapure Si and for polishing and lithographic patterning and etching of optical parts.

As with a number of glasses and crystalline optical materials, it is possible to form strong physical bonds between two planar or conformal silicon surfaces.  One advantage of this direct Si$-$Si bonding of macroscopic optical parts is that it facilitates the manufacture of complex optical subsystems, for example double-convex aspheres, combinations of lenses, prisms, and transmission gratings, and pairs of gratings oriented at right angles \cite{2012SPIE.8450E..2TV, 2010SPIE.7739E.123G}.  A second important advantage is that a sufficiently close bond is optically lossless, an important consideration not only for its effect on throughput but also because it can eliminate concerns about optical ghosts.  The remaining advantages of bonding stem from various difficulties encountered in antireflection coating a high index material in the near and mid-infrared:  There is a limited choice of index-matching materials, in particular at longer wavelengths.  Systems often are used at cryogenic temperatures and considerations of differential thermal expansion, brittleness and hygroscopic properties can restrict the choice of coatings even further. It is hard to get good antireflection performance across broad spectral ranges and at a range of incidence angles.

There are several good reviews of Si bonding that include accounts of the history of the field and a description of process alternatives, metrology, and problems \cite{1998AnRMS..28..215G,Masteika2014}.  The foundation paper on Si bonding came in 1986 \cite{1986JAP....60.2987S}. After that, there was a sequence of papers that used IR imaging to look for evidence of defects in the bond. Stengl et al. (1988) and G{\"o}esele et al. (1995) \cite{1988JaJAP..27L2364S, 1995ApPhL..67.3614G} directly monitored the bond propagation with time-lapse IR imaging. Lehman et al. 1989 and Goesele et al. \cite{1989JaJAP..28L2141L, 1995ApPhL..67.3614G} demonstrated gap-free bonding in a micro- cleanroom, in which the bonding process occurs immediately after a rinse-spin-vacuum cycle inside of a vacuum enclosure.  Other authors investigated the growth of bubbles at bond interfaces with time and the elimination of some or all of these bubbles after annealing bonded parts at temperatures of $800-1100\;^\circ$C \cite{Horn2009, Masteika2014}.

The chemistry of the bonding interface began to be understood with infrared absorption spectroscopy and multiple internal reflection spectroscopy\cite{feijoo1994}, which lent credibility to the idea of distinct temperature phases and evidence for Si$-$H bonds\cite{1995ApPhA..61..101R}.  These results ultimately helped to flesh out a robust picture of the chemistry as a function of anneal temperature\cite{1996JaJAP..35.2102R, 1998AnRMS..28..215G}.  Other variables potentially affecting bond strength were studied, for example surface roughness\cite{JJAP.37.4197}, surface topography \cite{2001JOptA...3...85G}, surface preparation\cite{1996ApPhL..68.2222T}, annealing time \cite{2000JAP....88.4404H}, ambient pressure and substrate thickness \cite{1995ApPhL..67..863G, 2007ApOpt..46.6793H}, and moisture and defects \cite{2001JAP....89.6013L}.  Notably, \cite{JJAP.37.4197} found that surface roughness above 1.3 nm RMS results in poor bonding quality in their sample of wafers etched with Argon.  Greco \emph{et al.} examined the role of surface topography in determining the the bonding strength of thick optical surfaces.  These authors showed that van der Waals interactions by themselves were consistent with their available experimental evidence, but they could not rule out other forces and phenomena.  The dearth of measurements of the mean separation between contacted surfaces hindered the unambiguous identification of the forces at play in bonded, rough surfaces \cite{2001JOptA...3...85G}.

@@

For all types of gaps and bubbles, our technique needs to provide an accurate assessment of the transmission loss at the operating wavelength.  For finite-sized bubbles, measurement of the axial dimension helps us to assess the effects of high-temperature annealing \cite{Horn2009, Masteika2014} on removal of hydrogen bubbles.  A wavelength-dependent transmission variation can also indicate the presence of large numbers of gaps that are too small to resolve spatially, as one might expect if there are many very small contaminants present along the interface.  Our technique must be able to characterize gaps with losses of a few percent at the operating wavelength.  A $2\;\%$ loss at $1.25\;\mu$m corresponds to a gap of $>25\;$nm at normal incidence and the gap size for a loss of this magnitude scales linearly with wavelength.  We therefore need to be able to measure transmission as a function of wavelength to a fraction of a percent, including all systematic errors, for devices operating near $1\;\mu$m and to a somewhat looser standard for devices operating at longer wavelengths.

@@

Equipped with an observed spectrum and our mixture model, we constructed the likelihood function \cite{2013sdmm.book.....I}.  The measurement errors are strongly correlated as discussed in Section \ref{sec_aboutErrors}.  To handle the correlated measurement errors we use Gaussian process regression \cite{rasmussen2006gaussian, DFMgp}.  The Gaussian process takes into account the unknown but finite covariance structure by introducing a covariance matrix, $\boldsymbol{C}$ whose elements represent the correlations of each sample $i$ with every other sample $j$.  We parameterize the covariance matrix elements in the following way:

>>>>

Crystalline silicon is an excellent optical material for the infrared. Si has a high refractive index ($3.55-3.45$ from $\lambda = 1150-2500\;$nm at room temperature, \cite{2006SPIE.6273E..77F}) and superb transmission from slightly longer than the equivalent wavelength of its band gap ($\sim$1.15 $\mu$m) to about 6.5 $\mu$m \cite{PhysRev.108.268,PhysRev.78.178} and in the far-IR \cite{doi:10.1117/12.323764}.  It has adequate transmission  ($\alpha \sim 1$ cm$^{-1}$) for many purposes in the 18-30 $\mu$m region as well \cite{doi:10.1117/12.323764}.  There is an extensive industrial infrastructure for the production of ultrapure Si and for polishing and lithographic patterning and etching of optical parts.

As with a number of glasses and crystalline optical materials, it is possible to form strong physical bonds between two planar or conformal silicon surfaces.  One advantage of this direct Si$-$Si bonding of macroscopic optical parts is that it facilitates the manufacture of complex optical subsystems, for example double-convex aspheres, combinations of lenses, prisms, and transmission gratings, and pairs of gratings oriented at right angles \cite{2012SPIE.8450E..2TV,2010SPIE.7739E.123G}.  A second important advantage is that a sufficiently close bond is optically lossless, an important consideration not only for its effect on throughput but also because it can eliminate concerns about optical ghosts.  The remaining advantages of bonding stem from various difficulties encountered in antireflection coating a high index material in the near and mid-infrared:  There is a limited choice of index-matching materials, in particular at longer wavelengths.  Systems often are used at cryogenic temperatures and considerations of differential thermal expansion, brittleness and hygroscopic properties can restrict the choice of coatings even further. It is hard to get good antireflection performance across broad spectral ranges and at a range of incidence angles.

There are several good reviews of Si bonding that include accounts of the history of the field and a description of process alternatives, metrology, and problems \cite{1998AnRMS..28..215G,Masteika2014}.  The foundation paper on Si bonding came in 1986 \cite{1986JAP....60.2987S}. After that, there was a sequence of papers that used IR imaging to look for evidence of defects in the bond. Stengl et al. (1988) and G{\"o}esele et al. (1995) \cite{1988JaJAP..27L2364S,1995ApPhL..67.3614G} directly monitored the bond propagation with time-lapse IR imaging. Lehman et al. 1989 and Goesele et al. \cite{1989JaJAP..28L2141L,1995ApPhL..67.3614G} demonstrated gap-free bonding in a micro- cleanroom, in which the bonding process occurs immediately after a rinse-spin-vacuum cycle inside of a vacuum enclosure.  Other authors investigated the growth of bubbles at bond interfaces with time and the elimination of some or all of these bubbles after annealing bonded parts at temperatures of $800-1100\;^\circ$C \cite{Horn2009,Masteika2014}.

The chemistry of the bonding interface began to be understood with infrared absorption spectroscopy and multiple internal reflection spectroscopy\cite{feijoo1994}, which lent credibility to the idea of distinct temperature phases and evidence for Si$-$H bonds\cite{1995ApPhA..61..101R}.  These results ultimately helped to flesh out a robust picture of the chemistry as a function of anneal temperature\cite{1996JaJAP..35.2102R,1998AnRMS..28..215G}.  Other variables potentially affecting bond strength were studied, for example surface roughness\cite{JJAP.37.4197}, surface topography \cite{2001JOptA...3...85G}, surface preparation\cite{1996ApPhL..68.2222T}, annealing time \cite{2000JAP....88.4404H}, ambient pressure and substrate thickness \cite{1995ApPhL..67..863G,2007ApOpt..46.6793H}, and moisture and defects \cite{2001JAP....89.6013L}.  Notably, \cite{JJAP.37.4197} found that surface roughness above 1.3 nm RMS results in poor bonding quality in their sample of wafers etched with Argon.  Greco \emph{et al.} examined the role of surface topography in determining the the bonding strength of thick optical surfaces.  These authors showed that van der Waals interactions by themselves were consistent with their available experimental evidence, but they could not rule out other forces and phenomena.  The dearth of measurements of the mean separation between contacted surfaces hindered the unambiguous identification of the forces at play in bonded, rough surfaces \cite{2001JOptA...3...85G}.

@@

For all types of gaps and bubbles, our technique needs to provide an accurate assessment of the transmission loss at the operating wavelength.  For finite-sized bubbles, measurement of the axial dimension helps us to assess the effects of high-temperature annealing \cite{Horn2009,Masteika2014} on removal of hydrogen bubbles.  A wavelength-dependent transmission variation can also indicate the presence of large numbers of gaps that are too small to resolve spatially, as one might expect if there are many very small contaminants present along the interface.  Our technique must be able to characterize gaps with losses of a few percent at the operating wavelength.  A $2\;\%$ loss at $1.25\;\mu$m corresponds to a gap of $>25\;$nm at normal incidence and the gap size for a loss of this magnitude scales linearly with wavelength.  We therefore need to be able to measure transmission as a function of wavelength to a fraction of a percent, including all systematic errors, for devices operating near $1\;\mu$m and to a somewhat looser standard for devices operating at longer wavelengths.

@@

Equipped with an observed spectrum and our mixture model, we constructed the likelihood function \cite{2013sdmm.book.....I}.  The measurement errors are strongly correlated as discussed in Section \ref{sec_aboutErrors}.  To handle the correlated measurement errors we use Gaussian process regression \cite{rasmussen2006gaussian,DFMgp}.  The Gaussian process takes into account the unknown but finite covariance structure by introducing a covariance matrix, $\boldsymbol{C}$ whose elements represent the correlations of each sample $i$ with every other sample $j$.  We parameterize the covariance matrix elements in the following way:
